---
title: "Gun Violence in the U.S."
author: " Stephanie Liu (sliu39@uw.edu), Daphne He (daphnehe@uw.edu), Cecelia Thomas (ceceliat@uw.edu)"
date: "Autumn 2022"
output: html_document
---

```{r setup, include=FALSE}
source("../source/chart2.R")
source("../source/calculations.R")
source("../source/table.R")
source("../source/chart1.R")
source("../source/chart3.R")
knitr::opts_chunk$set(echo = TRUE)
```

### Dynamic paragraph

Of the gun death victims from 1985 to 2018, `r victims_less_than_one()` were less than one years old. The percentage of male offenders is `r male_offenders_percentage()`% and the percentage of female offenders is `r female_offenders_percentage()`%. The percentage of Black victims is `r black_victim_percentage()`%. The percentage of gun deaths caused by handguns is `r handgun_used_percentage()`%. Through these values, we can see various trends in the data that show the severity of gun violence in the U.S.

``` {r echo=FALSE}
library("knitr")
kable(gender)
```
From the table seen above, we can see that most mass shootings are done by males (over 200). Females account for the least number of mass shootings (only 9). However, we need to note that the table does not account for people who identify outside of the gender binary, and therefore the data may have limitations or inaccuracies.
``` {r echo=FALSE}
#chart1
pie_chart
```
This visualization represents the type of weapon used to commit gun violence crimes. Handguns seem to have the highest usage, while rifles have the lowest usage. However, the data also accounts for any unknown weapons used in a crime, so the data may have inaccuracies in the amount of any certain type of weapon used.

```{r echo=FALSE}
#chart2
line_chart
```
This visualization 

``` {r echo=FALSE}
#chart3, shootings per state, bar chart
chart3
```

This visualization represents the number of shootings per state, including the District of Columbia, from the years 2013-2022. This chart further illustrates which states gun incidents have occurred most often. Illinois, California, Texas, and Florida are seen to have had the most gun related incidents from 2013 to 2022.